The Clinicopathological Features and Survival Outcomes of Patients with Different Metastatic Sites in Stage IV Endometrial Cancer:A SEER-Based Cohort Study

### 2025-03-08 code/eda-code/edamz.qmd
Part 2 addressed issue2 based on Dr. @andreashandel comments. #2

```{r}
summary_df = skimr::skim(mydata)
print(summary_df)
# save to file
summarytable_file = here("results", "edatables", "edasummarytable.rds")
saveRDS(summary_df, file = summarytable_file)
```

>>>>

```{r}
summary_df = skimr::skim(mydata)
print(summary_df)
# save to file
summarytable_file = here("results", "edatables", "edasummarytable.rds")
saveRDS(summary_df, file = summarytable_file)
```
```{r}
# Create a structured summary table
var_summary <- mydata %>%
  summarise_all(class) %>%
  pivot_longer(cols = everything(), names_to = "Variable", values_to = "Type") %>%
  mutate(Unique_Values = sapply(mydata, function(x) length(unique(x))),
         Missing_Values = sapply(mydata, function(x) sum(is.na(x))))

# Print the table to verify
print(var_summary)

# Save the structured table in a readable format
summarytable_file = here("results", "edatables", "edasummarytable2.rds")
saveRDS(var_summary, file = summarytable_file)
```

### 2025-03-08 code/processing-code/processingcodemz.qmd
Part 2 addressed issue2 based on Dr. @andreashandel comments. #2

# data loading
I am loading the raw data for further cleaning and processing 
```{r}
# path to data
# note the use of the here() package and not absolute paths
data_location <- here::here("data","raw-data","rawdata.csv")
rawdata <- readr::read_csv(data_location)
```
# Check Data

@@

skimr::skim(d1)  # Check changes
```
## Converting Categorical Variables to Factor

@@

We apply this conversion to the following variables:
- **Sex** and **Race-related variables** to ensure demographic information is handled correctly.
- **Cancer staging and metastasis indicators** to ensure proper classification.
- **Cause of death and survival indicators** to maintain categorical consistency.
```{r}
d2 <- d1 %>% dplyr::mutate(
    Sex = as.factor(Sex),
    `Race recode (W, B, AI, API)` = as.factor(`Race recode (W, B, AI, API)`),
    `Origin recode NHIA (Hispanic, Non-Hisp)` = as.factor(`Origin recode NHIA (Hispanic, Non-Hisp)`),
    `Race and origin recode (NHW, NHB, NHAIAN, NHAPI, Hispanic)` = as.factor(`Race and origin recode (NHW, NHB, NHAIAN, NHAPI, Hispanic)`),
    `Derived AJCC Stage Group, 7th ed (2010-2015)` = as.factor(`Derived AJCC Stage Group, 7th ed (2010-2015)`),
    `SEER Combined Mets at DX-bone (2010+)` = as.factor(`SEER Combined Mets at DX-bone (2010+)`),
    `SEER Combined Mets at DX-brain (2010+)` = as.factor(`SEER Combined Mets at DX-brain (2010+)`),
    `SEER Combined Mets at DX-liver (2010+)` = as.factor(`SEER Combined Mets at DX-liver (2010+)`),
    `SEER Combined Mets at DX-lung (2010+)` = as.factor(`SEER Combined Mets at DX-lung (2010+)`),
    `Mets at DX-Distant LN (2016+)` = as.factor(`Mets at DX-Distant LN (2016+)`),
    `COD to site recode` = as.factor(`COD to site recode`),
    `SEER cause-specific death classification` = as.factor(`SEER cause-specific death classification`),
    `SEER other cause of death classification` = as.factor(`SEER other cause of death classification`),
    `Survival months flag` = as.factor(`Survival months flag`),
    `COD to site rec KM` = as.factor(`COD to site rec KM`),
    `Vital status recode (study cutoff used)` = as.factor(`Vital status recode (study cutoff used)`)
)

skimr::skim(d2)
```
## Removing Patients in Specific Age Categories

@@

```{r}
d3 <- d2 %>% dplyr::filter(!`Age recode with <1 year olds` %in% c("01-04 years", "15-19 years"))
skimr::skim(d3)
```
## Including Patients with Stage IVA and IVB

@@

```{r}
d4 <- d3 %>% dplyr::filter(`Derived AJCC Stage Group, 7th ed (2010-2015)` %in% c("IVA", "IVB"))
skimr::skim(d4)
```
## Excluding Patients with Specific SEER Cause-Specific Death Classification

@@

```{r}
d6 <- d5 %>% dplyr::filter(!is.na(`Survival months`))
skimr::skim(d6)
```
## All done, data is clean now.

>>>>

# data loading

I am loading the raw data for further cleaning and processing

```{r}
# path to data
# note the use of the here() package and not absolute paths
data_location <- here::here("data","raw-data","rawdata.csv")
rawdata <- readr::read_csv(data_location)
```

# Check Data

@@

skimr::skim(d1)  # Check changes
```

## Converting Categorical Variables to Factor

@@

We apply this conversion to the following variables: - **Sex** and **Race-related variables** to ensure demographic information is handled correctly. - **Cancer staging and metastasis indicators** to ensure proper classification. - **Cause of death and survival indicators** to maintain categorical consistency.

```{r}
d2 <- d1 %>% dplyr::mutate(
    Sex = as.factor(Sex),
    `Race recode (W, B, AI, API)` = as.factor(`Race recode (W, B, AI, API)`),
    `Origin recode NHIA (Hispanic, Non-Hisp)` = as.factor(`Origin recode NHIA (Hispanic, Non-Hisp)`),
    `Race and origin recode (NHW, NHB, NHAIAN, NHAPI, Hispanic)` = as.factor(`Race and origin recode (NHW, NHB, NHAIAN, NHAPI, Hispanic)`),
    `Derived AJCC Stage Group, 7th ed (2010-2015)` = as.factor(`Derived AJCC Stage Group, 7th ed (2010-2015)`),
    `SEER Combined Mets at DX-bone (2010+)` = as.factor(`SEER Combined Mets at DX-bone (2010+)`),
    `SEER Combined Mets at DX-brain (2010+)` = as.factor(`SEER Combined Mets at DX-brain (2010+)`),
    `SEER Combined Mets at DX-liver (2010+)` = as.factor(`SEER Combined Mets at DX-liver (2010+)`),
    `SEER Combined Mets at DX-lung (2010+)` = as.factor(`SEER Combined Mets at DX-lung (2010+)`),
    `Mets at DX-Distant LN (2016+)` = as.factor(`Mets at DX-Distant LN (2016+)`),
    `COD to site recode` = as.factor(`COD to site recode`),
    `SEER cause-specific death classification` = as.factor(`SEER cause-specific death classification`),
    `SEER other cause of death classification` = as.factor(`SEER other cause of death classification`),
    `Survival months flag` = as.factor(`Survival months flag`),
    `COD to site rec KM` = as.factor(`COD to site rec KM`),
    `Vital status recode (study cutoff used)` = as.factor(`Vital status recode (study cutoff used)`)
)

skimr::skim(d2)
```

## Removing Patients in Specific Age Categories

@@

```{r}
d3 <- d2 %>% dplyr::filter(!`Age recode with <1 year olds` %in% c("01-04 years", "15-19 years"))
skimr::skim(d3)
```

## Including Patients with Stage IVA and IVB

@@

```{r}
d4 <- d3 %>% dplyr::filter(`Derived AJCC Stage Group, 7th ed (2010-2015)` %in% c("IVA", "IVB"))
skimr::skim(d4)
```

## Excluding Patients with Specific SEER Cause-Specific Death Classification

@@

```{r}
d6 <- d5 %>% dplyr::filter(!is.na(`Survival months`))
skimr::skim(d6)
```

## All done, data is clean now.

### 2025-03-08 products/manuscript/Manuscript.qmd
Part 2 addressed issue2 based on Dr. @andreashandel comments. #2

```{r}
#| label: tbl-summarytable
#| tbl-cap: "Data summary table."
#| echo: FALSE
resulttable=readRDS(here("results","edatables","edasummarytable.rds"))
knitr::kable(resulttable)
```

>>>>

```{r}
#| label: tbl-summarytable
#| tbl-cap: "Data summary table."
#| echo: FALSE
resulttable=readRDS(here("results","edatables","edasummarytable2.rds"))
knitr::kable(resulttable)
```
